\section*{Problem 1}

(Injective horseshoe lemma)
Suppose \(0 \to N_1 \to N_2 \to N_3 \to 0\)
is a s.e.s of \(R\)-modules.

Suppose there are injective resolutions
\(N_1 \to I_1^\bullet\)
and
\(N_3 \to I_3^\bullet\).

Then
prove that there is an injective resolution
\(N_2 \to I_2^\bullet\)
that fits into a short exact sequence of complexes
\[0 \to I_1^\bullet \to I_2^\bullet \to I_3^\bullet \to 0\]

compatible with \(0 \to N_1 \to N_2 \to N_3 \to 0\).


%-----------------------------------------------------------
\subsection*{Lemmata}

\begin{lemma}\label{lem-prod-inj}
  Let \(I_1, I_2\) be injective \(R\)-modules. \(I_1 \oplus I_2\) is injective.
\end{lemma}
\begin{proof}
  Let \(0 \to M \xrightarrow{f} N\) be an exact sequence of \(R\)-modules.
  And suppose that there is a map \(g: M \to I_1 \oplus I_2\).
  Let \(\pi_k: I_1 \oplus I_2 \to I_k\) be a natural projection for \(k = 1, 2\).
  Let \(g_k = \pi_k \circ g\) for \(k = 1, 2\).
  Since each \(I_k\) are injective, there is an extension \(h_k: N \to I_k\)
  such that \(g_k = h_k \circ f\).
  Then, let \(h: N \to I_1 \oplus I_2: x \mapsto (h_1(x), h_2(x))\).
  Trivially, it's a homomorphism as a composition of homomorphisms.
  \(h\) is an extension of \(g\), because for \(m \in M\),
  \[h(f(m)) = (h_1(f(m)), h_2(f(m))) = (g_1(m), g_2(m)) = g(m)\].
  Therefore, \(I_1 \oplus I_2\) is also injective.
\end{proof}


%-----------------------------------------------------------
\subsection*{Proof}

\[
\begin{tikzcd}
& 0 \ar{d} & 0 \ar{d} & 0 \ar{d} & \\
0 \ar{r} & M' \ar["i"]{r} \ar["g_0"]{d} & M \ar["p"]{r} \ar[dashed, "f_0"]{d} & M'' \ar{r} \ar["h_0"]{d} & 0 \\
0 \ar{r} & I'^0 \ar["\iota_0"]{r} \ar["g_1"]{d} & I^0 = I'^0 \oplus I''^0 \ar["\pi_0"]{r} \ar[dashed,"f_1"]{d} & I''^0 \ar{r} \ar["h_1"]{d} & 0 \\
0 \ar{r} & I'^1 \ar["\iota_1"]{r} \ar["g_2"]{d} & I^1 = I'^1 \oplus I''^1 \ar["\pi_1"]{r} \ar[dashed,"f_2"]{d} & I''^1 \ar{r} \ar["h_2"]{d} & 0 \\
 & \vdots& \vdots & \vdots &
\end{tikzcd}
\]

Suppose that the exact sequence \(0 \to M' \to M \to M'' \to 0\) with \(i, p\), 
an injective resolution \(M' \to I'^\bullet\), \(M'' \to I''^\bullet\) with \(g_k, h_k\)
were given as above diagram.

As the Problem 1, take \(I^k = I'^k \oplus I''^k\) for \(k \in \bbZ^{\ge 0}\).
Each \(I^k\) is injective by Lemma \ref{lem-prod-inj}.
Let \(\iota_k: I'^k \to I^k\) and \(\pi_k: I^k \to I''^k\) be natural homomorphisms.

Let's define \(f_k: I^{k - 1} \to I^k\).

First,
note that \(i\), \(\iota_0\) and \(g_0\) are injective because of exact sequences.
Because \(I'^0\) is injective, there is an extension \(\alpha_1: M \to I'^0\) of \(g_0\) such that \(g_0 = i \circ \alpha_1\).
Let \(f_0: M \to I^0\) be \(f_0: m \mapsto (\alpha_1(m), h_0(p(m)))\).

Then, \(0 \to M \xrightarrow{f_0} I^0\) is exact.
If \(f_0(m) = (0, 0)\) for some \(m \in M\),
\(\alpha_1(m) = 0\) and \(h_0(p(m)) = 0\).
Since \(h_0\) is injective, \(p(m) = 0\), and \(m \in \ker p = \im i\).
Let \(x \in M'\) such that \(i(x) = m\).
\(0 = f_0(m) = f_0(i(x)) = \iota_0(g_0(x))\).
Since \(\iota_0\) is injective, \(g_0(x) = 0\).
Since \(g_0\) is injective, \(x = 0\).
Therefore, \(m = i(x) = 0\).
This shows \(\ker f_0 = \{0\}\) and \(f_0\) is injective.

By Snake Lemma (See Problem 7), \(\coker g_0 \xrightarrow{\tilde \iota_0} \coker f_0 \to \coker{\tilde \pi_0} h_0\) is exact, where \(\tilde\iota_0\) and \(\tilde\pi_0\) are naturally induced from \(\iota_0\) and \(\pi_0\).
Also, \(\tilde\pi_0\) is surjective as \(\pi_0\) is surjective.
Also, since \(\ker h_0 = \im 0 = 0\), \(0 = \ker h_0 \to \coker g_0 \to \coker f_0\) is exact.
Because \(\im g_0 = \ker g_1\) and \(\im h_0 = \ker h_1\),
we can build the below diagram with the induced injective homomorphisms \(\tilde g_1: \coker g_0 = I'^0 / \ker g_1 \to I'^1\) and \(\tilde h_1: \coker h_0 = I''^0 / \ker h_1 \to I''^1\) which obtained from \(g_1\) and \(h_1\):
\[
\begin{tikzcd}
& 0 \ar{d} & 0 \ar{d} & 0 \ar{d} & \\
0 \ar{r} & \coker g_0 \ar["\tilde \iota_0"]{r} \ar["\tilde g_1"]{d} & \coker f_0 \ar["\tilde \pi_0"]{r} \ar[dashed, "\tilde f_1"]{d} & \coker h_0 \ar{r} \ar["\tilde h_1"]{d} & 0 \\
0 \ar{r} & I'^1 \ar["\iota_1"]{r} \ar["g_2"]{d} & I^1 = I'^1 \oplus I''^1 \ar["\pi_1"]{r}  & I''^1 \ar{r} \ar["h_2"]{d} & 0 \\
 & \vdots&  & \vdots &
\end{tikzcd}
\]
Note that each rows and the first and third column of above diagram is exact.
In this case, we can repeat what we did above,
just considering \(\coker f_0\), \(\coker g_0\), \(\coker h_0\) as \(M\), \(M'\), \(M''\).
Then, we can construct \(\tilde f_1: \coker f_0 \to I^1\) using the injectivity of \(I'^1\),
and an exact sequcne \(0 \to \coker g_1 \to \coker f_1 \to \coker h_1 \to 0\),
and \(\tilde f_2: \coker f_1 \to I^2\),
\(\cdots\).

Then, let \(f_k: I^{k - 1} \to I^k\) such as \(f_k(x) = \tilde f_k(x + \im f_{k - 1})\) for each \(k \in \bbZ^{\ge 0}\) (Let's assume \(I^{-1} = M\), \(I^{-2} = 0\) and \(f_{-2} = 0\) for convenience).
Then, since each \(\tilde f_k\) is injective, \(\tilde f_k (x) = 0\) iff \(x = \im f_{k - 1}\).
It implies \(\ker f_k = \im f_{k - 1}\).

Therefore, \(I^\bullet\) is an injective resolution of \(M\).
\qedsq
